---
title: "Introduction to chevreul"
author: 
  - name: Your name
    affiliation:
    - Your institution
    email: your.email@somewhere.com
output: 
  BiocStyle::html_document:
    self_contained: yes
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: show
date: "`r doc_date()`"
package: "`r pkg_ver('chevreul')`"
vignette: >
  %\VignetteIndexEntry{Introduction to chevreul}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}  
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    crop = NULL ## Related to https://stat.ethz.ch/pipermail/bioc-devel/2020-April/016656.html
)
```

# Basics

## Install `chevreul`

You can install `r Biocpkg("chevreul")` by using the following commands in your `R` session:

```{r "install", eval = FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE)) {
    install.packages("BiocManager")
}

BiocManager::install("chevreul")

## Check that you have a valid Bioconductor installation
BiocManager::valid()
```

## Asking for help

Ask for help at [Bioconductor support site](https://support.bioconductor.org/). Remember to use the `chevreul` tag and check [the older posts](https://support.bioconductor.org/tag/chevreul/). Other alternatives are available such as creating GitHub issues and tweeting. However, please note that if you want to receive help you should adhere to the [posting guidelines](http://www.bioconductor.org/help/support/posting-guide/).

## Citing `chevreul`

We hope that `r Biocpkg("chevreul")` will be useful for your research. Please use the following information to cite the package and the overall approach. Thank you!

```{r "citation"}
## Citation info
citation("chevreul")
```

# Quick start to using `chevreul`

```{r "start", message=FALSE}
library("chevreul")
```


`R` session information.

```{r reproduce3, echo=FALSE}
## Session info
library("sessioninfo")
options(width = 80)
session_info()
```
